%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\usepackage{fontspec}
\usepackage{fontawesome5}

\begin{document}
\header{neil}{johari}
{\faDesktop\hspace{.2cm} software engineer}


% In the aside, each new line forces a line break
\begin{aside}
    \section{contact}
    \href{tel:+15165328612}{(516) 532-8612}
    \href{mailto:njohari@umich.edu}{njohari@umich.edu}
    \href{mailto:neil@johari.tech}{neil@johari.tech}
    \href{https://johari.tech/}{https://johari.tech/}
    \section{favorite technologies}
    git
    vim
    tmux
    \section{programming languages}
    Ruby
    Java 
    C++
    MATLAB
    Python
    ArduinoC
    \section{current courses}
    CS Pragmatics
    Physics 240
    Engineering 100
    Statistics 250
    \section{courses taken}
    Differential Eqns.
    Engineering 101
    Physics 140
\end{aside}

\section{education}

\begin{entrylist}
    \educationentry
    {2018 - 2022}
    {B.S.E. {\normalfont in Computer Science}}
    {Ann Arbor, MI}
    {University of Michigan College of Engineering}
    {GPA: 4.0/4.0}
    \educationentry
    {2014 - 2018}
    {Diploma {\normalfont with highest honors and Mastery in Science}}
    {Syosset, NY}
    {Syosset High School}
    {GPA: 8.636/8.0}

\end{entrylist}

\section{experience}
\begin{entrylist}
    \entry
    {2014 - now}
    {Website Developer}
    {\href{https://syosseths.com}{https://syosseths.com}}
    {Selected to lead design and implementation of the new Syosset Senior High School’s website utilizing Ruby on Rails, MongoDB, and Redis (2017-now). \\ 
    Responsible for 280+ commits with 24,000+ changes. Project was started from scratch, open sourced with MIT License, and features extensive permission system and administrative backend.}
    \entry
    {2014 - 2018}
    {Researcher}
    {\href{https://neiljohari.page.link/ml}{https://neiljohari.page.link/ml}}
    {Successfully developed a machine learning model to analyze MRI scans of Alzheimer’s disease patients (2016-2018). \\
        Created a model of video game hours played due to social influence with an analysis through machine learning (2015-2016). \\
    Conducted literary research on sleep deprivation (2014-2015).}
\end{entrylist} 

\section{open source side projects }
\begin{entrylist}
    \entry
    {2016 - now}
    {Scram}
    {\href{https://github.com/neiljohari/scram}{https://github.com/neiljohari/scram}}
    {Programmed a transparent Ruby permissions system gem with MongoDB integration.}
    \entry
    {2014 - 2015}
    {Mongoid Forums}
    {\href{https://github.com/NJayDevelopment/mongoid_forums}{https://github.com/NJayDevelopment/mongoid\_forums}}
    {Developed a Ruby on Rails gem for forums with MongoDB integration.}
    \entry
    {2012 - 2014}
    {AutoBroadcaster+}
    {\href{https://dev.bukkit.org/projects/abp}{https://dev.bukkit.org/projects/abp}}
    {Published a server-wide scheduled broadcasting plugin for Minecraft. Downloaded 227k+ times.}

\end{entrylist}
\section{awards}
\begin{entrylist}
    \entry
    {2018}
    {Nassau County Legislature Citation}
    {}
    {In recognition of leadership and community engagement.} 
    \entry
    {2018}
    {Bernie Goudreau Memorial Award}
    {}
    {In recognition of achievement in mathematics and computer science.}
    \entry
    {2017}
    {1st Place at Andromeda, 2nd Place at WAC Invitational}
    {}
    {Awarded for the creation of a machine learning model to analyze MRI scans of Alzheimer’s disease patients using convolutional neural networks.}
    \entry
    {2015}
    {Gold Medal at Al Khalfus Math Fair}
    {}
    {Awarded for the creation of a
    model of video game hours played due to social influence with an analysis through machine learning.}
\end{entrylist}

\end{document}
